week getbackontrack

### 2024-10-27 week5-2.Rmd
getbackontrack

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

@@

#save the output of your function
test <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))

@@

# STUDY CHAPTER 12 of RSiena Manual!

>>>>

# Week 5-2
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

![](images/you-krilled-him.jpg)

@@

```{r}
#save the output of your function
test <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = "sociology", 
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))

@@

# STUDY CHAPTER 12 of RSiena Manual! 
# COLLECTIVELY SEND PAPER TO JOCHEM BEFORE WEEKEND!
# PrACTICE WITH RSIENA 
# LOOK AT MANUAL

# DONT GO OVERBOARD!!! 
# REMAIN FOCUSED!!!

### 2024-10-27 week5.Rmd
datapracticew5
getbackontrack

---
title: "Week 5 - Chapter 7 pt.1 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Notes while discussing other peeps plots

>>>>

---
title: "Week 5 - Chapter 7 pt.1 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
---
# Week 5-1
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
::: {.column width="50%"}
![](images/krill-yourself.jpg)
:::

# Notes while discussing other peeps' plots

### 2024-10-27 week6.Rmd
getbackontrack

---
title: "Week 6"
author: "Verooo"
date: "2024-10-09"
output: html_document
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

>>>>

---
title: "Week 6"
author: "Verooo"
date: "2024-10-09"
output: html_document
---
# Week 6
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

### 2024-10-27 weekbacktrack.Rmd
getbackontrack

## Parts fo project

@@

tentative deadline: Saturday, 16.11.24

>>>>

## Project parts

@@

tentative deadline: Saturday, 23.11.24

+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
| Mon                                                                | Tue                                            | Wed                                                           | Thu                                                                   | Fri                                                                      | Sat                                                                                     | Sun                                      |
+:===================================================================+:===============================================+:==============================================================+:======================================================================+:=========================================================================+:========================================================================================+:=========================================+
| 28\.                                                               | 29\.                                           | 30\.                                                          | 31\.                                                                  | 01.11.                                                                   | 02\.                                                                                    | 03\.                                     |
|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
| ![](images/used_arson%20frog.jpg)                                  | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/socialnetworking.jpg){width="800"}Clarify RQs [D]\ | ![](images/socialnetworking_meh.jpg){width="800"}Intro and theory [W] | ![](images/socialnetworking.jpg){width="800"}Intro and theory [W]\       | ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]                       | ![](images/Trixie-joke.jpg){width="800"} |
|                                                                    |                                                | & Clarify design [D]                                          |                                                                       | Clarify [D] & define data [S1]                                           |                                                                                         |                                          |
+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
| 04\.                                                               | 05\.                                           | 06\.                                                          | 07\.                                                                  | 08\.                                                                     | 09\.                                                                                    | 10\.                                     |
|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
| ![](images/socialnetworking_meh.jpg){width="800"}Define data [S1]\ | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking_meh.jpg){width="800"}\                    | ![](images/socialnetworking.jpg){width="800"}Initial description [S3]\   | ![](images/socialnetworking.jpg){width="800"}Plotting                                   | ![](images/Trixie-joke.jpg){width="800"} |
| & create effects structure [S2]                                    |                                                |                                                               | Create effects structure [S2]\                                        | & plotting                                                               |                                                                                         |                                          |
+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
| 11\.                                                               | 12\.                                           | 13\.                                                          | 14\.                                                                  | 15\.                                                                     | 16\.                                                                                    | 17\.                                     |
|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
| ![](images/socialnetworking_meh.jpg){width="800"}Plotting          | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking.jpg){width="800"}Specify model [S4]\      | ![](images/socialnetworking.jpg){width="800"}Data & methods [W]          | ![](images/socialnetworking.jpg){width="800"}Estimate model [S5] & goodness of fit [S6] | ![](images/Trixie-joke.jpg){width="800"} |
|                                                                    |                                                |                                                               | Data & methods part [W]                                               |                                                                          |                                                                                         |                                          |
+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+
| 18\.                                                               | 19\.                                           | 20\.                                                          | 21\.                                                                  | 22\.                                                                     | **23.**                                                                                 | 24\.                                     |
|                                                                    |                                                |                                                               |                                                                       |                                                                          |                                                                                         |                                          |
| ![](images/socialnetworking_meh.jpg){width="800"}Results [W]       | ![](images/used_arson%20frog.jpg){width="952"} | ![](images/used_arson%20frog.jpg)                             | ![](images/socialnetworking_meh.jpg){width="800"}Finish results [W]   | ![](images/socialnetworking.jpg){width="800"}Discussion & conclusion [W] | ![](images/socialnetworking.jpg){width="800"}Read over project & hand in!               | ![](images/Trixie-joke.jpg){width="800"} |
+--------------------------------------------------------------------+------------------------------------------------+---------------------------------------------------------------+-----------------------------------------------------------------------+--------------------------------------------------------------------------+-----------------------------------------------------------------------------------------+------------------------------------------+

: Days overview

**Legend**

::: columns
::: {.column width="50%"}
![social network plot (color) = time for SNA (obvious... or not?)](images/socialnetworking.jpg){width="80"}

![social network plot (muted) = not a lot of time for SNA, but SOME](images/socialnetworking_meh.jpg){width="80"}
:::

::: {.column width="50%"}
![arson = otherwise busy/NO time for SNA](images/used_arson%20frog.jpg){width="80"}

![you think this is a joke? = chores, admin work, and mental breakdowns/ NO time for SNA](images/Trixie-joke.jpg){width="80"}
:::
:::

[D] = task refers to research design

[S#] = task refers to step of analysis

[W] = task refers to writing the report

### Timeline Question

When is plotting done in this progression? At the initial description part or earlier?

## Project Planning

I have decided to drop another course I was taking and focus on the deadline of this course.

I think the workload of both courses' deadlines exceeds my capacities, especially since the courses of PER 3 already start on 04.11. and I also have duties relating to my board year simultaneously.

### Suggestions for Jochem:

I will update you once a week to inform you of my progress. This can act as an "accountability-measure" and pushes me to face some struggles head-on, that I would otherwise try to avoid. It also creates a predesignated time to discuss the project, which can help me ask questions I would otherwise deem "not important enough to reach out to you". \
I propose that I write you an email about the **current state of affairs on Mondays**, since I cannot work on the project on Tuesday and Wednesday anyways and that gives you some time to reply. Please let me know if this is okay for you. \
In your reply I would appreciate input on how to move on in case I am facing a hurdle that "stalls" the project's progress, and I also welcome redirection if I seem to get "lost in the sauce". Any hints on how to take "shortcuts" that I was not aware of are also very much invited (e.g. "I know of this online resource that is about *exactly* this issue.").
